Rubin Observatory Pointing Algorithm and Simulations

### 2025-02-01 ms.tex
motion plots put in

Times for altitude, azimuth, and rotational motions are calculated using a constant acceleration value and maximum velocity (configurable for each component). A finite value for the jerk can be included based on \citet{Mu2009}, but is turned off by default as it has minimal impact on the total motion times.--xxx is this actually true? Looks like we do have jerk on for telescope motions.

xxx--Cable wrap is tracked for the telescope (which can go xxx) and the camera which has limits of xxx.

xxx-figures with starting/ending values, colored by time, for each component.

@@

There are concerns that LEO satellite mega-constellations could impact ground based astronomical observatories. We have not included any satellite dodging as earlier work found that even for an Gen 2 Starlink constellation with 30,000 satellites, only 0.04\% of LSST science pixels would be lost to satellite streaks \citep{Hu2022} (xxx-tech note too).

>>>>

The times for the altitude, azimuth and rotational motions are calculated using a constant acceleration value and maximum velocity (configurable for each component). A finite value for the jerk can be included based on \citet{Mu2009}, but is turned off by default as it has minimal impact on the total motion times.--xxx is this actually true? Looks like we do have jerk on for telescope motions.

Figure~\ref{fig:motion_times} shows the motion times for different slews. For short slews of a few degrees, the telescope is usually the limiting factor. For longer slews, the dome or optics loops are the limiting factors.

Cable wrap is tracked for the telescope which can go -250 to 250 degrees in azimuth and the camera rotator which has limits of -90 to 90 degrees.

\begin{figure}
    \epsscale{0.7}
    \plotone{plots/motion_times}
    \epsscale{1}
    \caption{Kinematic motion times for different components.  \label{fig:motion_times}}
\end{figure}

@@

There are concerns that LEO satellite mega-constellations could impact ground based astronomical observatories. We have not included any satellite dodging as earlier work found that even for a Gen 2 Starlink constellation with 30,000 satellites, only 0.04\% of LSST science pixels would be lost to satellite streaks \citep{Hu2022, Yoachim2025}.
